### 2020-10-15 priority-gv.tex
Moved closed progress to the appendices.

Canonical forms deviate from those for GV, in that we opt to move all $\nu$-binders to the top. The standard GV canonical form, alternating $\nu$-binders and their corresponding parallel compositions, does not work for PGV, since multiple channels may be split across a single parallel composition:
\begin{compacttheorems}
  \begin{definition}[Canonical Forms]
    \label{def:pgv-canonical-forms}
    A~configuration $\tm{\conf{C}}$ is in canonical form if it is of the following form, where no term $\tm{M_i}$ is a value:
    \[
      \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;N)}}}
    \]
  \end{definition}
  \begin{restatablelemma}{lempgvcanonicalforms}[Canonical Forms]
    \label{lem:pgv-canonical-forms}
    If $\cseq[\main]{\ty{\Gamma}}{\conf{C}}$, there exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}}\equiv\tm{\conf{D}}$ and $\tm{\conf{D}}$ is in canonical form.
  \end{restatablelemma}
  \begin{proof}
    We move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, discard any superfluous occurrences of $\tm{\child\;\unit}$ using \LabTirName{SC-ParNil}, and move the main thread to the rightmost position using \LabTirName{SC-ParComm} and \LabTirName{SC-ParAssoc}.
  \end{proof}
\end{compacttheorems}

A~configuration either reduces, or it is equivalent to configuration in normal form. Crucial to the normal form is that each term $\tm{M_i}$ is blocked on the corresponding channel $\tm{x_i}$, and hence no two terms act on dual endpoints. Furthermore, no term $\tm{M_i}$ can perform a communication action by itself, since those are excluded by the definition of actions:
\begin{compacttheorems}
  \begin{definition}[Normal Forms]
    A~configuration $\tm{\conf{C}}$ is in normal form if it is of the following form, where each $\tm{M_i}$ is ready to act on $\tm{x_i}$:
    \[
      \tm{\conf{C}}
      \equiv
      \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;V)}}},
    \]
  \end{definition}
  \begin{restatabletheorem}{thmpgvclosedprogressconfs}[Progress, $\cred$]
    \label{lem:pgv-closed-progress-confs}
    If $\cseq[\main]{\emptyenv}{\conf{C}}$ and $\tm{\conf{C}}$ is in canonical form, then either $\tm{\conf{C}}\cred\tm{\conf{D}}$ for some $\tm{\conf{D}}$; or $\tm{\conf{C}\equiv\conf{D}}$ for some $\tm{\conf{D}}$ in normal form.
  \end{restatabletheorem}
  \input{prf/thm-pgv-closed-progress-confs}
\end{compacttheorems}

Finally, as a corollary from closed progress, we get that well-typed terms which do not return endpoints must return \emph{only} a value:
\begin{corollary}
  \label{cor:pgv-closed-progress}
  If $\cseq[\main]{\emptyenv}{\conf{C}}$, $\tm{\conf{C}}\centernot\cred$, and $\tm{\conf{C}}$ contains no endpoints, then $\tm{\conf{C}}\equiv\tm{\phi\;V}$ for some value V.
\end{corollary}

>>>>

Canonical forms deviate from those for GV, in that we opt to move all $\nu$-binders to the top. The standard GV canonical form, alternating $\nu$-binders and their corresponding parallel compositions, does not work for PGV, since multiple channels may be split across a single parallel composition.

A~configuration either reduces, or it is equivalent to configuration in normal form. Crucial to the normal form is that each term $\tm{M_i}$ is blocked on the corresponding channel $\tm{x_i}$, and hence no two terms act on dual endpoints. Furthermore, no term $\tm{M_i}$ can perform a communication action by itself, since those are excluded by the definition of actions.
Finally, as a corollary, we get that well-typed terms which do not return endpoints return \emph{just} a value:

\begin{compacttheorems}
  \begin{definition}[Canonical Forms]
    \label{def:pgv-canonical-forms}
    A~configuration $\tm{\conf{C}}$ is in canonical form if it is of the following form, where no term $\tm{M_i}$ is a value:
    \[
      \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;N)}}}
    \]
  \end{definition}
  \begin{definition}[Normal Forms]
    A~configuration $\tm{\conf{C}}$ is in normal form if it is of the following form, where each $\tm{M_i}$ is ready to act on $\tm{x_i}$:
    \[
      \tm{\conf{C}}
      \equiv
      \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;V)}}},
    \]
  \end{definition}
  \begin{restatabletheorem}{thmpgvclosedprogressconfs}[Progress, $\cred$]
    \label{thm:pgv-closed-progress-confs}
    If $\cseq[\main]{\emptyenv}{\conf{C}}$ and $\tm{\conf{C}}$ is in canonical form, then either $\tm{\conf{C}}\cred\tm{\conf{D}}$ for some $\tm{\conf{D}}$; or $\tm{\conf{C}\equiv\conf{D}}$ for some $\tm{\conf{D}}$ in normal form.
  \end{restatabletheorem}
  \begin{proof}
    Our proof follows the reasoning by Kobayashi~\cite{kobayashi06} used in the proof of deadlock freedom for closed processes (Theorem 2). Details are in~\Cref{prf:thm-pgv-closed-progress-confs}.
  \end{proof}
  \begin{corollary}
    \label{cor:pgv-closed-progress}
    If $\cseq[\main]{\emptyenv}{\conf{C}}$, $\tm{\conf{C}}\centernot\cred$, and $\tm{\conf{C}}$ contains no endpoints, then $\tm{\conf{C}}\equiv\tm{\phi\;V}$ for some value V.
  \end{corollary}
\end{compacttheorems}
